### 2019-01-25 abstract.tex
ssr

Several researchers have studied 
a class of Boolean functions, 
called \textbf{nested canalyzing functions} (NCFs),
which are used to model certain biological 
phenomena \cite{Kauffman-1969,Kauffman-etal-2003,Kauffman-etal-2004}.
We study the relationships between NCFs and symmetric 
Boolean functions. Our results ...

>>>>

A class of Boolean functions, 
called \textbf{nested canalyzing functions} (NCFs),
has been used to model certain biological phenomena.
Rearchers have studied some properties of these functions
such as sensitivity and stability.
In this note, we examine the relationships between NCFs and symmetric 
Boolean functions. 
We identify all NCFs that are also symmetric. 
We also consider a more general form of symmetric Boolean functions
called $r$-symmetric functions, where $r$ is the symmetry level.
We show how one can get lower and upper bounds on the symmetry
level of an NCF $f$ given a suitable respresentation of $f$.
